Constant Rate Computational Fuzzy Extractors

### 2014-01-08 trunk/constantRate/ConstCompFuzzExt.tex
Notation file

For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.  In the information-theoretic setting these two parameter are at odds.  Any increase error-tolerance requires a similar increase to the entropy of the source.  However, this does not need to be the case in the computational setting.  The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The difference is a computational fuzzy extractor outputs a pseudorandom key. }  In this setting an error tolerance \emph{larger} than the starting entropy may be possible.  We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.  In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.   This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}

Our construction is based on obfuscation.  While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.  This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.  Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).  Dodis and Smith constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.  Unfortunately, our construction is not a noisy point obfuscation and leaks partial information about particular blocks of the source.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  However, we will use codes that only correct unidirectional errors~(see \secref{sec:coding theory}).

@@

Here we present relevant definitions of fuzzy extractors.  We focus on the notion of computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.  Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.  The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.  We will also use the standard notion of an average-case extractor. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \ell, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\ell, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

The question is we ask is for what type of sources can we build fuzzy extractors?  Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.  The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.  When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.  We ask whether security is possible when $gap$ is small or negative.
%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.  %We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.  As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch.  Instead, we will use a computational fuzzy extractor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).  We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):

\begin{definition}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' (\gen) and ``reproduce'' (\rep) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

\begin{lemma}
\label{lem:cond and ext}
Let $\epsilon_{ent} >0$ be a parameter.  Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.  Let $\ext:\mathcal{M}_2\times \zo^*\rightarrow \zo^\ell$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.  Define the $\gen, \rep$:
\begin{itemize}
\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
\end{itemize}
Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \ell, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
\end{lemma}
\begin{proof}
Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
\end{proof}

\subsection{Coding Theory}
\label{sec:coding theory}
We introduce some notions from the field of binary error correcting codes.  Usually the class of errors considered is all points within Hamming distance at most $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but never bit flips from $1\not\rightarrow 0$.
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
\end{definition}
\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.

@@

\begin{definition}
A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
\end{definition}
All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).  This is only true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.

\begin{lemma}
Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
\end{lemma}
\begin{proof}
Suppose there is some $i$ that is not equiprobable.  Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$. First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$. First suppose that $0<|C_{i_1}| < |C_{i_0}|$.  Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.  Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.  This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.  This completes the proof.
Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.  This is a contradiction and completes the proof.
\end{proof}

@@

We present the notion of virtual black-box obfuscation with the weakening that the simulator produces an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the.runtime of $A$ and $S$ must be polynomial in the length of their first input.
\end{enumerate}
\end{definition}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(C(w_i))$.
\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$.  \\
\,
Let $p_i = \mathcal{O}(C(r_i))$.
\item Let $r = \ext(c, seed)$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p, seed)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
\subitem Else set $c_i' = 1$.
\item Set $c = \decode$.
\item Output $r  = \ext (c', seed)$.
\end{enumerate}
\vspace{0.45in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

\textbf{Notes:}  We make several observations about the above construction:
\begin{itemize}
\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.  As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
\item There are two possible reasons for a bit of $c_i'$ to be $1$.  Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.  However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(see~\cite[Section 3.3]{fuller2013computational} for discussion).
\end{itemize}

Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.  The adversary is provided with equality oracles for each block individually.  Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.  We begin with the setting where each block is independent and then move to the setting of correlated blocks.

>>>>

For a fixed length key, there are two main parameters: the desired error tolerance and the required entropy of the source.  In the information-theoretic setting these two parameter are at odds.  Any increase error-tolerance requires a similar increase to the entropy of the source.  However, this does not need to be the case in the computational setting.  The notion of computational fuzzy extractors was introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.\footnote{The only difference between a computational fuzzy extractor and a fuzzy extractor is the key is pseudorandom instead of statistically random. }  With computational security, an error tolerance \emph{larger} than the starting entropy may be possible.  We provide the first construction of a fuzzy extractor where the entropy of the source distribution is smaller than the desired error-tolerance.\footnote{Security is impossible if all points of the source distribution are close together.  In the fuzzy extractor setting, a necessary condition for security is that a negligible portion of the source distribution lies in within any error-tolerance region.   This is both a necessary and sufficient condition for security in the interactive setting using two-party computation.}

Our construction is based on obfuscation.  While black-box obfuscation of polynomial time functions is known to be impossible~\cite{barak2001possibility}, we use the obfuscation of point functions.  This class is known to be achievable under particular number-theoretic assumptions~\cite{canetti1997towards} and generically from generic cryptographic hardness assumptions~\cite{wee2005obfuscating}.

\textbf{Overview of Construction:}  Consider a source $w = w_1,..., w_\ell$ that is split into blocks.  We would like to construct tolerate Hamming errors for individual blocks.  The main idea is for each block, $i$: either the $w_i$ is obfuscated or a random point $r_i$ is obfuscated~(this idea is similar to the construction of digital lockers from point obfuscation).  Then with a close value $w'$ the recovery value knows where random values were obfuscated and where $w_i$ was obfuscated.  To tolerate errors, the choice of obfuscating $w_i$ or a random point is made using bits of an error correcting code.

\textbf{Connection with Noisy Point Obfuscation: } Ideally, our construction would be a noisy point obfuscation~(which is a strictly stronger object than a computational fuzzy extractor).  Unfortunately, this is not the case.  Since each block is individual obfuscated, equality of individual blocks is learned~(for sources where not all blocks have high entropy).  This precludes virtual black-box~(VBB) security where no partial information about the input may be learned.  Dodis and Smith~\cite{DBLP:conf/stoc/DodisS05} constructed noisy point obfuscation when the source entropy is significantly higher than the error-tolerance.  Constructing VBB obfuscation for sources where the error tolerance is smaller than the starting entropy is an important open question.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For our sources, we consider the Hamming metric, for two vectors $x, y$ over $\mathcal{Z}^n$ the Hamming distance between $x,y$ is $d(x,y) = \{i | x_i \neq y_i\}$.  For the Hamming metric, $|B_t(\cdot)| = \sum_{i=0}^t {n \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  However, we will use codes that only correct one-sided errors~(see \secref{sec:coding theory}).

@@

Here we present relevant extractor definitions.  We start with the standard notion of an average-case extractor. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

We focus on computational fuzzy extractors introduced by Fuller, Meng, and Reyzin~\cite{fuller2013computational}.  Definitions for information-theoretic fuzzy extractors and secure sketches can be found in the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}.  The definition of computational fuzzy extractors allows for a small probability of error, as described in~\cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

@@

\begin{definition}[Computational Fuzzy Extractor]\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
Any efficient fuzzy extractor is also a computational fuzzy extractor with the same parameters.  
Note that in the above definition of fuzzy extractors, the errors are chosen before $P$ is known: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness.
For notational convenience, we the definition of computational fuzzy extractors specifies a general class of sources for which the fuzzy extractor is designed to work, rather than the class of sources that consists of all sources of a given min-entropy $m$~(of course, this modification can also be applied to prior definitions of information-theoretic secure sketches and fuzzy extractors).

Our main question is: for what type of sources can we build fuzzy extractors?  Of particular interest are sources where information-theoretic bounds do not allow meaningful constructions~\cite[Lemmas C.1 and C.2]{DBLP:journals/siamcomp/DodisORS08}.  The main limiting factor is the difference between the starting entropy and the size of the ball to be corrected or $gap = \Hoo(W) - \log |B_t(\cdot)$.  When $gap$ is large, information-theoretic fuzzy extractors provide a good solution.  We ask whether security is possible when $gap$ is small or negative.
%In this paper, we ask whether a smaller entropy loss can be achieved by considering a computational fuzzy extractor with a computational security requirement.  %We therefore relax the security requirement of \defref{def:fuzzy extractor} to require a pseudorandom output instead of a truly random output.

As in the information-theoretic realm~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}, a computational fuzzy extractor can be constructed by combining a correction component and an privacy-amplication component.  As shown in Fuller, Meng, and Reyzin~\cite[Corollary 3.8 and Theorem 3.10]{fuller2013computational}, the ``right'' correction component is probably not a computational version of a secure sketch~\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}.  Instead, we will use a computational fuzzy conductor~(this is a computational analogue of the notion introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).  We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case~(see \defref{def:hill ent}):

\begin{definition}
\label{def:comp fuzzy cond}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' (\gen') and ``reproduce'' (\rep') is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
\begin{itemize}
\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

\begin{lemma}
\label{lem:cond and ext}
Let $\epsilon_{ent} >0$ be a parameter.  Let $\gen'$, $\rep'$ be a $(\mathcal{M}_1, \mathcal{W}, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ and outputs in $\mathcal{M}_2$.  Let $\ext:\mathcal{M}_2\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m} - \log 1/\epsilon_{ent}, \epsilon_{ext})$-average case extractor.  Define the $\gen, \rep$:
\begin{itemize}
\item $\gen(w; r, x):$ run $(y, p')= \gen'(w; r)$ and set $p = (p', x)$ and $r = \ext(y; x)$,  and output $(r, p)$.
\item $\rep(w, (p', x)):$ recover $y = \rec'(w'; p')$ and output $r = \ext(y; x)$. 
\end{itemize}
Then $\gen, \rep$ is a $(\mathcal{M}_1, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{sec}+\epsilon_{ext}+\epsilon_{ent}, s_{sec} - |\ext|)$-hard with error $\delta$.
\end{lemma}
\begin{proof}
Result of extractibility of conditional HILL entropy~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}.\bnote{I don't think you need this $\epsilon_{ent}$ should be able to just use average case extractor directly}
\end{proof}

\subsection{Coding Theory}
\label{sec:coding theory}
We introduce some notions from the field of binary error correcting codes.  Usually the standard class of errors  is all points within Hamming distance $t$, we will use the Hamming analog of the $Z$-channel where there are flips from $0\rightarrow 1$ but no bit flips from $1\not\rightarrow 0$.
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$. 
\end{definition}
\textbf{Note:} Any code that corrects $t$ Hamming errors corrects $t$ $0\rightarrow 1$ errors, but more efficient codes may be exist for these errors.

@@

\begin{definition}
A binary $(\neigh_t, \epsilon_{code})$ code is output equiprobable\bnote{Find the right name for this} $\forall i, |\{C | C_i =1\}| =|C|/2$.
\end{definition}
All binary linear codes~(without constant bits) are output equiprobable and there exist constant rate output equiprobable codes that correct errors for $t = O(\ell)$~(first constructed by Justesen~\cite{justesen1972class}).  This is true as long as $C$ contains no constant bits.  Usually, if a code has constant bits, we can truncate those bits before encoding and obtain a code with better parameters.  For the remainder of this work when we say a code, we assume there are no constant bits.

\begin{lemma}
Let $C$ be a \emph{linear} binary code with no constant bits.  Then $C$ is output equiprobable.
\end{lemma}
\begin{proof}
Suppose there is some $i$ that is not equiprobable.  Let $C_{i_1} = \{C | C_i =1\}$ and $C_{i_0} = \{C | C_i = 0\}$. First note that since $C$ does not have any constant bits, it dimension is at least $1$ yielding that $|C| = 2^k$ for some $k$. First suppose that $0<|C_{i_1}| < |C_{i_0}|$.  Let $c\in C_{i_1}$ then by linearity $\forall c'\in C_{i_0}$, $c\oplus c' \in C_{i_1}$.  Furthermore, for all distinct $c_1, c_2\in C_{i_0}$, $c_1\oplus c \neq c_2\oplus c$.  This means that $|C_{i_i}|\geq |C_{i_0}|$ as all $c'\oplus c$ must be distinct and contained in $C_{i_1}$.  
Now suppose that $|C_{i_1}| > |C_{i_0}| >0$, denote the elements of $C_{i_1}$ by $c_1,..., c_{|C_{i_1}|}$, then by linearity $c_1\oplus c_2, c_1\oplus c_3,..., c_1\oplus c_{|C_{i_1}|}$ are all distinct elements of $C_{i_0}$ this means that $|C_{i_0}|\geq |C_{i_1}| -1 $, for the total size to be even this means that $|C_{i_0}|\geq |C_{i_1}|$.  This is a contradiction and completes the proof.
\end{proof}

@@

We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}  Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$, 
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability ver the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}.
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$.
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$, 
and for all binary predicates $\pi$, 
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
\end{enumerate}
\end{definition}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Let $r = \ext(c, seed)$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p, seed)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
\subitem Else set $c_i' = 1$.
\item Set $c = \decode$.
\item Output $r  = \ext (c', seed)$.
\end{enumerate}
\vspace{0.45in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

\textbf{Notes:}  We make several observations about the above construction:
\begin{itemize}
\item If $C$ is output equiprobable, in expectation, half of $w$ is information-theoretically unknown conditioned on $p$.  As described in~\cite[Section 3.3]{fuller2013computational} some type of lossiness is necessary to avoid coding bounds.
\item There are two possible reasons for a bit of $c_i'$ to be $1$.  Because the true value was $1$~(there is little chance of $1$ being incorrectly decoded as $0$ assuming $w_i'$ is independent of the sketch) and because $w_i \neq w_i'$.  However if a bit of $c_i'$ is $0$ this likely means that $w_i=w_i'$ because collisions when the $c_i=0$ are unlikely~(occurring with probability roughly $2^{-n}$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips, instead of a code that corrects all Hamming weight $t$ errors.
\item The extractor can be removed from the construction leaving a computational fuzzy conductor~(\defref{def:comp fuzzy cond}).
\end{itemize}

\subsection{Security of Construction}
Assuming virtual black-box obfuscation, we can argue security in the presence of equality oracles for each block.  The adversary is provided with equality oracles for each block individually.  Security rests on an adversaries inability to learn the values using only \emph{adaptive} equality queries.  For illustrative purposes, we begin with the setting where blocks are independent and each have super-logarithmic entropy and then move to the setting of correlated blocks with some entropy deficient blocks.
